Indexing Variation Graphs\footnote{This work was supported by the Wellcome Trust grant [098051].}

### 2016-04-17 paper/paper.tex
Clafifications

The following definitions are useful when discussing text indexes and path indexes.

@@

De~Bruijn graphs are a special case of pruned de~Bruijn graphs. Hence we may compress a de~Bruijn graph structurally by repeatedly merging sets of nodes sharing a common prefix of their keys, as long as the conditions of Lemma~\ref{lemma:dbg-prune} hold.

@@

These are both based on ST, which requires a maximally pruned DBG

@@

\begin{proof}[Proof of Lemma~\ref{lemma:dbg-prune} (Pruning)]
Let $G_{d} = (V_{d}, E_{d})$ be the \orderk{k} de~Bruijn graph of $G$, let $G'' = (V'', E'')$ be the path graph corresponding to the new key set, and let $\mathcal{S}$ be the \kcollection{k} used for building the path graphs. Each node $v'' \in V''$ is an equivalence class of nodes $V_{d}(v'') \subseteq V_{d}$ corresponding to a shared prefix $G''.\gkey(v'')$ of keys. For all $v \in V_{d}(v'')$, we have $G_{d}.\gvalue(v) = G''.\gvalue(v'')$.

@@

(c) If $\abs{X} = 0$, every key prefix-matches the pattern. If $\abs{X} = 1$, set $G'.\find(X)$ is the set of nodes $v' \in V'$ with $G'.\glabel(v') = X[0]$. Now assume that $\abs{X} \ge 2$ and that $G'.\gkey(v')$ prefix-matches $X[1, \abs{X}-1]$ for all $v' \in G'.\find(X[1, \abs{X}-1])$. By (a), there is at most one node $u' \in G'.\gpred(v', X[0])$ for each such node $v'$. By (b), key $G'.\gkey(u')$ is a prefix of $X[0] \cdot G'.\gkey(v')$. Because $X[1, \abs{X}-1]$ prefix-matches $G'.\gkey(v')$, pattern $X$ prefix-matches string $X[0] \cdot G'.\gkey(v')$, and hence the pattern must prefix-match key $G'.\gkey(u')$.
\end{proof}

>>>>

The following definitions are useful when discussing path indexes.

@@

We can compress a de~Bruijn graph structurally by repeatedly merging sets of nodes sharing a common prefix of their keys, as long as the conditions of Lemma~\ref{lemma:dbg-prune} hold. Let $G_{d} = (V_{d}, E_{d})$ be the \orderk{k} de~Bruijn graph of graph $G$, and let $G' = (V', E')$ be a pruned de~Bruijn graph produced by that process. Each node $v' \in V'$ is an \emph{equivalence class} of nodes $V_{d}(v') \subseteq V_{d}$ corresponding to a shared prefix $G'.\gkey(v')$ of keys. For all $v \in V_{d}(v')$, we have $G_{d}.\gvalue(v) = G'.\gvalue(v')$.

@@

Path graphs; LCP array; compact trie of keys; LCP interval tree

@@

\begin{proof}[Proof of Lemma~\ref{lemma:dbg-prune} (Pruning)]
Let $G_{d} = (V_{d}, E_{d})$ be the \orderk{k} de~Bruijn graph of $G$, let $G'' = (V'', E'')$ be the path graph corresponding to the new key set, and let $\mathcal{S}$ be the \kcollection{k} used for building the path graphs.

@@

(c) If $\abs{X} = 0$, every key prefix-matches the pattern. If $\abs{X} = 1$, set $G'.\find(X)$ is the set of nodes $v' \in V'$ with $G'.\glabel(v') = X[0]$. Now assume that $\abs{X} \ge 2$ and that $G'.\gkey(v')$ prefix-matches $X[1, \abs{X}-1]$ for all $v' \in G'.\find(X[1, \abs{X}-1])$. By (a), there is at most one node $u' \in G'.\gpred(v', X[0])$ for each such node $v'$. By (b), key $G'.\gkey(u')$ is a prefix of $X[0] \cdot G'.\gkey(v')$. Because $X[1, \abs{X}-1]$ prefix-matches $G'.\gkey(v')$, pattern $X$ prefix-matches string $X[0] \cdot G'.\gkey(v')$, and hence the pattern must prefix-match key $G'.\gkey(u')$.

Note that any key set satisfying (a) and (b) also satisfies (c). If $G'' = (V'', E'')$ is a pruned de~Bruijn graph and $v'' \in V''$ is a node, any pattern matching node $v''$ prefix-matches the key of the corresponding equivalence class in graph $G'$.
\end{proof}
